### 2024-04-26 README.Rmd
Update README.Rmd

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Title of your paper goes here"
```

@@

> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

@@

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

You can download the compendium as a zip from from this URL:
[master.zip](/archive/master.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- finally, open `analysis/paper/paper.Rmd` and knit to produce the `paper.docx`, or run `rmarkdown::render("analysis/paper/paper.qmd")` in the R console

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Chert use and procurement patterns during the Upper Palaeolithic in Southwesternmost Iberia"
```

@@

> Belmiro, J., Terradas, X., Dominguez-Bella, S., Cascalheira, J., (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

@@

> Belmiro, J., Terradas, X., Dominguez-Bella, S., Cascalheira, J., (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.17605/OSF.IO/DBFT2>

@@

You can download the compendium as a zip from this URL:
[master.zip](/archive/master.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- finally, open `analysis/paper/paper.Rmd` and knit to produce the `paper.docx`, or run `rmarkdown::render("analysis/paper/paper.qmd")` in the R console
